\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
cleaning the paper adding some extra info

Fig.\ref{fig:simple_case} describes the starting point of the simulations that will follow. Fluid $1$ is from the left hand side of the formation. Later, different mobility ratios and different regions of various permeabilities will be introduced, but for now only few of these initial and boundary conditions will be applied. Boundary conditions will include a no-slip condition for the upper and lower boundary inlet is place at the left hand side while outlet on th right hand side of the domain. Initial conditions include initial values of velocity and pressure in the left and right hand side of the domain respectively. Also for different cases we have different geometrical domain aspect ratios, number of elements and types of grid (fixed and usntructured or adaptive and unstructured mesh).

@@

\medskip
In Fig.\ref{fig:1a_homoheleshaw_3}(a), there is the description of the domain. Three different cases with different set-ups will follow. The first one is the homogeneous domain where permeability $K_{1}=1.e-10$ everywhere while for the heterogeneous case the following permeabilities have been introduced, $K_{1}=(1.e-10 \;to\; 5.e-10$), $K_{2}=1.e-10$, $K_{3}=(1.e-11 \;to\; 5.e-10)$ and $K_{4}=(1.e-12 \;to\; 5.e-10)$. For the homogeneous case we use two different mobility ratios of $3$ and $10$ while we proceed to the heterogenous case using a mobility ratio of $10$.

>>>>

Figure \ref{fig:simple_case} describes the starting point of the simulations that will follow. Fluid $1$ is from the left hand side of the formation. Later, different mobility ratios and different regions of various permeabilities will be introduced, but for now only few of these initial and boundary conditions will be applied. Boundary conditions will include a no-slip condition for the upper and lower boundary inlet is place at the left hand side while outlet on th right hand side of the domain. Initial conditions include initial values of velocity and pressure in the left and right hand side of the domain respectively. Also for different cases we have different geometrical domain aspect ratios, number of elements and types of grid (fixed and usntructured or adaptive and unstructured mesh).

@@

\medskip
In fig.\ref{fig:1a_homoheleshaw_3}(a), there is the description of the domain. Three different cases with different set-ups will follow. The first one is the homogeneous domain where permeability $K_{1}=1.e-10$ everywhere while for the heterogeneous case the following permeabilities have been introduced, $K_{1}=(1.e-10 \;to\; 5.e-10$), $K_{2}=1.e-10$, $K_{3}=(1.e-11 \;to\; 5.e-10)$ and $K_{4}=(1.e-12 \;to\; 5.e-10)$. For the homogeneous case we use two different mobility ratios of $3$ and $10$ while we proceed to the heterogenous case using a mobility ratio of $10$.
